### 2020-02-08 method/sec_4-db_struct.tex
Updated future works

\subsection{Timeseries Key Attributes}
- Module ID
  String field which describe the source of the data generated. Example of hec-hms, flow2d, weather-station etc
- Value Type
  - Scalar, Vector, Grid are the Value Types which are interested in the WDIAS.
- Location
  Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS.
  - Point locations - Contains a name which is human readable. lat and lon of the location on earth surface.
  \begin{lstlisting}[language=Python]
    {
        "locationId": "wdias-hanwella",
        "name": "Hanwella",
        "lat": 6.909722222,
        "lon": 80.08166667
    }
  \end{lstlisting}
  - Regular Grid locations - Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
  And the location of the first cell and the width and height of it.
  \begin{lstlisting}[language=Python]
      {
        "locationId": "wdias_kelani_basin",
        "description": "Kelani Basin",
        "rows": 120,
        "columns": 139,
        "geoDatum": "Kandawala",
        "gridFirstCell": {
            "firstCellCenter": {
                "x": 397074.0,
                "y": 504875.0
            },
            "xCellSize": 250.0,
            "yCellSize": 250.0
        }
    }
\end{lstlisting}
  - Irregular Grid locations (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)

@@

\subsection{MySQL}
Relational Database Management System (RDBMS).
SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
Since WDIAS scope is to using open source tools, it is using MySQL as persistent database for storing timeseries metadata described above.
One instance of MySQL is using only by adapter-metadata service.
Other than that, another instance of MySQL is using for adapter-extension which will be describe in more detail \ref{data_preprocess}.
MySQL is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
\ref{db_struct_redis} instance is using for caching the data from MySQL, since the MySQL database instances, itself not going to get much load.
Other than MySQL, there are many open source databases can be used to replace the same functionality.

\subsection{InfluxDB} \cite{influxdbInfluxDBDocumentation}
Open timeseries DB with MIT license
Support SQL-Like query language
Clustering available with a commercial version
Among the other timeseries open source databases available, InfluxDB has higher number of usage and support. Database is written in Golang programming language,
and has higher performance. Other than InfluxDB, another Database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the InfluxDB, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
InfluxDB can setup on a computer which will give the required performance. Going further, users can use commercial version of InfluxDB in order to gain more performance.

>>>>

\subsection{Timeseries Key Attributes}
\label{sub:timeseries_key_attributes}
- Module ID
  String field which describe the source of the data generated. Example of hec-hms, flow2d, weather-station etc
- Value Type
  - Scalar, Vector, Grid are the Value Types which are interested in the WDIAS.
- Location
  Location of the timeseries. All locations have unique String identifier called locationId. Further, there are two type of location types that is interested in the WDIAS.
  - Point locations - Contains a name which is human readable. lat and lon of the location on earth surface.
  \begin{lstlisting}[language=Python]
    {
        "locationId": "wdias-hanwella",
        "name": "Hanwella",
        "lat": 6.909722222,
        "lon": 80.08166667
    }
  \end{lstlisting}
  - Regular Grid locations - Contains a name which is human readable. The grid presents by dividing into equal size cells. Thus, it need the number of rows and columns. 
  And the location of the first cell and the width and height of it.
  \begin{lstlisting}[language=Python]
      {
        "locationId": "wdias_kelani_basin",
        "description": "Kelani Basin",
        "rows": 120,
        "columns": 139,
        "geoDatum": "Kandawala",
        "gridFirstCell": {
            "firstCellCenter": {
                "x": 397074.0,
                "y": 504875.0
            },
            "xCellSize": 250.0,
            "yCellSize": 250.0
        }
    }
\end{lstlisting}
  - Irregular Grid locations (endpoints are available with in the WDIAS system, but skipped since it is out of the interest of the scope.)

@@

\subsection{MySQL}
\label{sub:mysql}
Relational Database Management System (RDBMS).
SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
Since WDIAS scope is to using open source tools, it is using MySQL as persistent database for storing timeseries metadata described above.
One instance of MySQL is using only by adapter-metadata service.
Other than that, another instance of MySQL is using for adapter-extension which will be describe in more detail \ref{data_preprocess}.
MySQL is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
\ref{db_struct_redis} instance is using for caching the data from MySQL, since the MySQL database instances, itself not going to get much load.
Other than MySQL, there are many open source databases can be used to replace the same functionality.

\subsection{InfluxDB} \cite{influxdbInfluxDBDocumentation}
\label{sub:influxdb}
Open timeseries DB with MIT license
Support SQL-Like query language
Clustering available with a commercial version
Among the other timeseries open source databases available, InfluxDB has higher number of usage and support. Database is written in Golang programming language,
and has higher performance. Other than InfluxDB, another Database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the InfluxDB, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
InfluxDB can setup on a computer which will give the required performance. Going further, users can use commercial version of InfluxDB in order to gain more performance.

### 2020-02-08 summary/sec_2-future_work.tex
Updated future works

\section{Future Work}
- Lack of data prepossessing modules
- Supporting Irregular Grids
- Grid performance
- Define infrastructure as code - Teraform
- Improve test cases - correct RPS
- Further improve hierarchical database performance
- Add Alerting extension modules
- Add pubsub extension modules

>>>>

\section{Future Work}
This section discussed about the lacking features in the \acrshort{wdias}, and some of the improvement that can add for improve the performance and usability of the system.

\paragraph{Lack of data preprossessing modules}
The extension module enable plugin system to integrate prepossessing modules which can use for process the data which are inserted to the system or based on regular intervals. Also \acrshort{wdias} provide a more generic open interface approach to create more preprocessing modules. Since \acrshort{wdias} is an open source system, it expect more modules to be create by the community. When compared to other system like \acrshort{fews}, current system only have few extension for the testing purpose. This is one of the major area that need to be improved.

\paragraph{Supporting Irregular Grids}
At the moment \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints define for the implementation which can follow the same microservice architecture. The scope of the \acrshort{wdias} does not belong such level of implementation and the scope has reduced by removing such components from the system.

\paragraph{Grid data performance}
As mentioned in the \ref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. This has some performance issues as well as memory leak issues. Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN. They are some future work that can focus on improving the performance of grid data.

\paragraph{Define infrastructure as code}
Physical nodes for the \acrshort{k8s} cluster created using Cloud Computing provider such as \acrshort{eks}. And defining the each pod resource limitations at the helm chart level. But the infrastructure that need to deploy the \acrshort{wdias} can define as code such as using tools like Teraform which is independent of the Cloud Computing provider. Using such tool, users will able to easy deploy the \acrshort{wdias} on any Cloud provider without much hassle.

\paragraph{Improve test cases}
As described in detail with \ref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses Time Stepping Feedback loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment. But using that it is not possible to get desired \acrshort{rps} for each test case within the test plan.
Because of this issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning. Having create timeseries at the beginning causes some issues such as most of the thread are working on that test case rather on required test cases. Still there may be some improvement that can be done.

\paragraph{Further improve hierarchical database performance}
As further described in \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}. With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances. The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations. As an example, based on the key attribute \ref{sub:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.

\paragraph{Add Alerting extension modules}
At the moment, extensions only support On Change and On Time events. But it will be good to have event trigger support based on reconfigured alert level.

\paragraph{Add Publisher Subscriber extension modules}
The \acrshort{wdias} better to be capable of triggering external systems based on the events such as webhooks.
